An excess of positive results: Comparing the standard Psychology literature with Registered Reports

### 2021-03-10 preprint/positive_results_SRs_RRs.tex
Updated preprint to the accepted version of the manuscript (i.e., made a papaja "journal" mode version of positive_results_SRs_RRs_revision1.Rmd, and added a citation disclaimer box on the title page)

\usepackage{float}
\usepackage{framed}
\usepackage{caption}
\usepackage{setspace}
\captionsetup[figure]{font={stretch=1, small}, skip=10pt}
\captionsetup[textbox]{name=Box,labelsep=period,labelfont=it}
\newfloat{textbox}{thp}{lop}
\floatname{textbox}{Box}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[shorthands=off,main=british]{babel}
\else
  % load polyglossia as late as possible as it *could* call bidi if RTL lang (e.g. Hebrew or Arabic)
  \usepackage{polyglossia}
  \setmainlanguage[variant=british]{english}
\fi

@@

\abstract{
When studies with positive results that support the tested hypotheses have a higher probability of being published than studies with negative results, the literature will give a distorted view of the evidence for scientific claims. Psychological scientists have been concerned about the degree of distortion in their literature due to publication bias and inflated Type-1 error rates. Registered Reports were developed with the goal to minimise such biases: In this new publication format, peer review and the decision to publish take place before the study results are known. We compared the results in the full population of published Registered Reports in Psychology (\(N = 71\) as of November 2018) with a random sample of hypothesis-testing studies from the standard literature (\(N = 152\)) by searching 633 journals for the phrase `test* the hypothes*' (replicating a method by Fanelli, 2010). Analysing the first hypothesis reported in each paper, we found \(96\%\) positive results in standard reports, but only \(44\%\) positive results in Registered Reports. The difference remained nearly as large when direct replications were excluded from the analysis (\(96\%\) vs \(50\%\) positive results). This large gap suggests that psychologists under-report negative results to an extent that threatens cumulative science. Although our study did not directly test the effectiveness of Registered Reports at reducing bias, these results show that the introduction of Registered Reports has led to a much larger proportion of negative results appearing in the published literature compared to standard reports.
}

@@

If the scientific literature were a faithful representation of the research scientists conduct, a cumulative science would be a powerful tool to infer what is true about the world.
When random error is the only threat to the accuracy of individual findings, aggregating across many findings allows inferences about the presence and size of effects with a certain reliability.
But when published findings are systematically biased, cumulative science breaks down:
Unlike random error, bias does not cancel out when aggregating across studies -- in the worst case it accumulates, leading us away from the truth rather than towards it.
Unfortunately there are good reasons to believe that the Psychology literature is not a faithful representation of all research psychologists conduct.
For more than half a century, scientists have repeatedly noticed a suspiciously high \enquote{success} rate in Psychology:
Studying 362 empirical articles published in four Psychology journals in 1955/56, Sterling (1959) found that \(97.28\%\) of the studies that used significance tests rejected the null hypothesis.
A replication of this study performed on articles published in 1986/87 reported \(95.56\%\) statistically significant results (Sterling, Rosenbaum, \& Weinkam, 1995).
Similarly, a seminal study by Fanelli (2010) compared the literatures of 20 disciplines and found that \(91.5\%\) of papers published in Psychology reported support for their first hypothesis, the highest estimate of all disciplines in the study.
For these percentages to be a realistic representation of the research that psychologists perform, both statistical power and the proportion of true hypotheses (i.e., the prior probability that the null hypothesis is false) that are tested must exceed \(90\%\).
In other words: nearly all predictions researchers make must be correct, and either the studied effect sizes or the used sample sizes (given the same study design) must consistently be very large.

@@

Sterling (1959) already suspected a selection process behind the numbers he found:
\enquote{(\ldots{}) for psychological journals a policy exists under which the vast majority of published articles satisfy a minimum criterion of {[}statistical{]} significance} (p.~31).
This selection process is one of several kinds of biases that will lead to an inflation of positive results in the literature.
We can distinguish two broad categories of bias: \enquote{publication bias} and \enquote{questionable research practices}.
Publication bias describes publishing behaviours that give manuscripts that find support for their tested hypotheses a higher chance of being published than manuscripts that do not find support for their tested hypotheses.
These include editors and reviewers selectively rejecting manuscripts with negative results (``reviewer bias'', Greenwald, 1975; Mahoney, 1977) and researchers deciding not to submit studies with negative results for publication (``file-drawering''; Rosenthal, 1979).
Questionable research practices (QRPs) describe research behaviours that make the evidence in favour of a certain conclusion look stronger than it is (typically, though not always, leading to an inflated type-I error rate; see Lakens, 2019).
These include presenting unexpected results as having been predicted \emph{a priori} (HARKing, short for ``hypothesising after results are known''; Kerr, 1998) and exploiting flexibility in data analysis to obtain statistically significant results (``\emph{p}-hacking''; Simmons, Nelson, \& Simonsohn, 2011).
Evidence for both categories of bias exist:
Publication bias has been shown in peer review (Atkinson, Furlong, \& Wampold, 1982; Mahoney, 1977) and in longitudinal data from an NSF grant programme that found a file-drawering effect for studies with negative results (Franco, Malhotra, \& Simonovits, 2014, 2016); and QRPs have been admitted by scientists in several survey studies (Agnoli, Wicherts, Veldkamp, Albiero, \& Cubelli, 2017; Fiedler \& Schwarz, 2016; John, Loewenstein, \& Prelec, 2012).

Some have argued that selecting for statistically significant results is defensible -- desirable, even -- because it weeds out low-quality research that would only pollute the literature (Cleophas \& Cleophas, 1999; see also de Winter \& Happee, 2013; and van Assen, van Aert, Nuijten, \& Wicherts, 2014, for a critique).
How problematic selective publishing is in practice remains an empirical question:
If most negative results that are currently missing from the literature are the result of immature ideas or poorly conducted studies, we should expect that a literature in which studies are selected based on their quality but not based on their results would contain a similar proportion of positive results as the current one.
But how many positive results would such an unbiased literature contain in reality?
We set out to explore this question by comparing the rate of positive results in the current Psychology literature to studies published in a new format designed to minimise QRPs and publication bias: Registered Reports.

@@

An increasingly popular proposal to reduce bias is preregistration, where authors register a time-stamped protocol of their hypotheses, planned method, and analysis plan before data collection (for a historical overview, see Wiseman, Watt, \& Kornbrot, 2019).
Preregistration is thought to mitigate QRPs by preventing HARKing (hypotheses must be stated before the results are known) and by reducing the risk of \emph{p}-hacking via restricted flexibility in data analysis.
However, preregistration does not prevent file-drawering or reviewer bias and may thus be insufficient to fight publication bias (Goldacre et al., 2016; Rasmussen, Lee, \& Bero, 2009; but see Kaplan \& Irvin, 2015).
A more effective safeguard against both publication bias and QRPs is promised by Registered Reports (Chambers, 2013; Chambers, Dienes, McIntosh, Rotshtein, \& Willmes, 2015; Jonas \& Cesario, 2016; Nosek \& Lakens, 2014).
Registered Reports (RRs) are a new publication format with a restructured submission timeline:
Before collecting data, authors submit a study protocol containing their hypotheses, planned procedures, and analysis pipeline (typically in the form of an Introduction and Method section) to a journal.
The protocol undergoes peer review, and, if successful, receives \enquote{in-principle acceptance}, meaning that the journal commits to publishing the final article following data collection, regardless of the statistical significance of the results.
The authors then collect and analyse the data and complete the final report.
The final report undergoes another round of peer review, but this time only to ensure that the authors adhered to the registered plan and did not draw unjustified conclusions (and, if applicable, that the data pass pre-specified quality checks).
Registered Reports thus combine an antidote to QRPs (preregistration) with an antidote to publication bias, because studies are selected for publication before their results are known.
Since its introduction at the journal \emph{Cortex} in 2013, the format has rapidly gained popularity and is offered by 225 journals at the time of writing (\url{http://cos.io/rr}).

In addition to bias protection, Registered Reports promise high-quality research: Stage-1 (pre-data) peer review increases the likelihood that methodological flaws and immature or misguided ideas will be identified and addressed before a study is conducted, and authors typically have to include outcome-neutral control conditions that allow verifying data quality once results are in (studies failing these quality checks may be rejected).
Many journals offering Registered Reports also require that planned hypothesis tests are based on a power analysis that ensures a high probability of finding a statistically significant result if there is a true effect of the expected size (e.g., \(90\%\) power for a given effect size of interest\footnote{An overview of the requirements specified by each participating journal is available at \url{https://docs.google.com/spreadsheets/d/1D4_k-8C_UENTRtbPzXfhjEyu3BfLxdOsn9j-otrO870}}).

Assuming a constant alpha level, the rate of positive results in a literature (i.e., the proportion of supported hypotheses among all tested hypotheses) is influenced by three factors: the proportion of true hypotheses among all tested hypotheses, statistical power, and bias.
The Registered Reports format combines powerful safeguards against publication bias and QRPs with standards for research quality that are at least equal to ordinary peer review, and often include statistical power requirements that likely exceed those in the standard literature (see e.g., Maxwell, 2004; Singleton Thorn, Dudgeon, \& Fidler, 2019; Szucs \& Ioannidis, 2017).
Therefore, if the emerging Registered Reports literature in Psychology contains fewer positive results than the standard literature, the cause must be either the difference in bias or a lower proportion of true hypotheses tested in Registered Reports (or a combination of the two).
At this time, we have good reasons to believe in a difference in bias, but less reason to believe in a difference in the proportion of true hypotheses (at least regarding original work, see below), which would make bias a more plausible explanation of a potential difference in the positive result rate.
Considering the high standards for research quality in Registered Reports, a large difference in positive results between Registered Reports and the standard literature would also indicate that publication bias is not a desirable filter for poorly conducted studies, but that we should worry about high-quality negative results we are missing because of it.

@@

The goal of our study was to test if Registered Reports in Psychology show a lower positive result rate than articles published in the traditional way (henceforth referred to as \enquote{standard reports}, SRs), and to estimate the size of this potential difference.
We set out to replicate a study by Fanelli (2010) on a new sample of standard reports in Psychology and compared them to all published Registered Reports in Psychology.
Fanelli searched for articles containing the phrase \enquote{test\(^\ast\) the hypothes\(^\ast\)}, drew a random sample of 150 articles per discipline, and for each of these coded if the first hypothesis mentioned in the abstract or full text had been supported or not.
For standard reports we used the same sampling method (restricted to the Psychology discipline), and for Registered Reports we relied on a database curated by the Center for Open Science (COS).
We chose this method because Fanelli's 2010 and 2012 studies (both use the same coding method) have been highly influential, and his method can easily be applied to a large set of studies.
We additionally coded if studies were replications or original work because many published Registered Reports are replications.
If replications are motivated by scepticism of the original results, the prior probability of hypotheses tested in these studies may be lower than in original studies, which could lead to a larger proportion of negative results regardless of bias.

In a recent commentary on benefits and challenges of open-science practices for early-career researchers, Allen and Mehler (2019) conducted a similar investigation:
They coded the proportion of null results in the 127 biomedical and Psychology Registered Reports listed in the COS database as of September 2018.
We were not aware of their parallel efforts when we planned our study in September and October 2018.
Allen and Mehler used a self-developed method to code the percentage of unsupported hypotheses in Registered Reports (counting all hypotheses in each paper) and found \(60.5\%\) unsupported hypotheses across all included Registered Reports, \(66\%\) for replication attempts, and \(54.5\%\) for novel research.
They compared these numbers to an estimate of 5--20\(\%\) null results in the standard literature (based on data from Fanelli, 2012, who coded only the first hypothesis of each paper; and Cristea \& Ioannidis, 2018, who coded the percentage of statistically significant results in figures and tables of articles published in Nature, Science, and PNAS).

A major advantage of our study is that it allows us to draw a more meaningful comparison between Registered Reports and the standard literature because we apply a previously used method (Fanelli, 2010, 2012) to both groups.
In addition, we replicate Fanelli (2010) and provide data to evaluate his method: The search term \enquote{test\(^\ast\) the hypothes\(^\ast\)} might introduce selection effects, meaning that results obtained this way may not generalise to hypothesis-testing studies that do not use this phrase.
Therefore we also coded the phrases used to introduce hypotheses in Registered Reports, analysed how many of them would have been detected with Fanelli's search term, and compiled a list of alternative search terms to test the generalisability of Fanelli's results in the future.
Finally, we share a rich dataset containing the exact quotes of hypotheses and conclusions on which we based our judgements, as well as detailed descriptions of our sampling and coding procedure (see Appendix).
This allows others to verify (or contest) our results and may provide an interesting resource for future meta-scientific research.

@@

After conducting a pilot to test the planned procedure, we preregistered our study (\url{https://osf.io/s8e97}).
Methods and analyses described here were preregistered unless otherwise noted.
A detailed comparison of our preregistration and the eventual procedure is provided in the supplement.
We report how we determined our sample size, all data exclusions, and all measures in the study.

@@

We used the same method as Fanelli (2010) to obtain a new sample of standard reports, but restricted year of publication to 2013-2018 to match the sample to the Registered Reports population.
We excluded papers if they were incomplete, unpublished, or retracted articles (e.g., meeting abstracts, study protocols without results), if they did not test a hypothesis, or if they contained insufficient information to reach a coding decision.
An overview of the sampling process and all exclusions is shown in Figure~\ref{fig:sampling}.

For standard reports we downloaded a current version of the Essential Science Indicators (ESI) database (retrieved on 4th December 2018) and used Web of Science to search for articles published between 2013 and 2018 with a Boolean search query containing the phrase \enquote{test\(^\ast\) the hypothes\(^\ast\)} and the ISSNs of all 633 journals listed in the ESI Psychiatry/Psychology category.
Using the same sample size as Fanelli (2010), we randomly selected 150 papers from the 1919 search results using the sample() function in R and the seed \enquote{20190120} (seed was not preregistered, but no other seeds were tried).
We initially excluded eight papers and replaced them (decision to replace excluded papers was not preregistered) through the same random sampling procedure until 150 studies were found that met our criteria, but later found that two papers had been excluded erroneously, leading to a final sample size of 152 (see Fig.~\ref{fig:sampling}).

@@

For Registered Reports we aimed to include all published Registered Reports in the field of Psychology that tested at least one hypothesis, regardless of whether or not they used the phrase \enquote{test\(^\ast\) the hypothes\(^\ast\)}.
We downloaded a database of published Registered Reports curated by the Center for Open Science\footnote{\url{https://www.zotero.org/groups/479248/osf/items/collectionKey/KEJP68G9}} (retrieved on 19th November 2018), and excluded papers published in journals that were listed in categories other than \enquote{Psychiatry/Psychology} or \enquote{Multidisciplinary} in the ESI.
Note that the decision to focus only on the Psychiatry/Psychology category meant excluding 13 Registered Reports published in \emph{Cortex} because the ESI counts this journal towards the separate category \enquote{Neuroscience and Behavior}.
Papers published in multidisciplinary journals and in journals not included in the ESI (e.g., \emph{Royal Society Open Science}) were hand-coded by AS.
This deviates from our preregistration insofar as we had not specified how discipline membership would be determined.

Following these exclusions, we verified the Registered Reports status of all remaining papers in our sample.
Papers were counted as Registered Reports if they were labelled as such by the journal itself and the journal submission guidelines made it clear that these submissions had been reviewed and received in-principle acceptance before the data collection (or analyses) of all studies in the paper had been conducted (in accordance with \url{https://cos.io/rr}).
For papers not clearly labelled as Registered Reports, we consulted relevant editorial publications (e.g., for special issues) or contacted the respective editors directly.
Of the 151 entries in the COS Registered Reports database, 55 were excluded because they belonged to a non-Psychology discipline, 12 because we could not verify that they were Registered Reports, and 13 because they did not test hypotheses or contained insufficient information, leaving 71 Registered Reports for the final analysis (see Fig.~\ref{fig:sampling}).
Note that we excluded all eight \enquote{Registered Replication Reports} (RRRs; Simons, Holcombe, \& Spellman, 2014; Simons, 2018) in our sample because this format explicitly focusses on effect size estimation and not hypothesis testing (``Registered Replication Reports,'' n.d., decision was not preregistered).

@@

The main dependent variable was whether the first hypothesis was supported or not, as reported by the authors.
We tried to follow Fanelli's (2010) coding procedure as closely as possible, which he describes as follows:

\begin{quote}
By examining the abstract and/or full- text, it was determined whether the authors of each paper had concluded to have found a positive (full or partial) or negative (null or negative) support.
If more than one hypothesis was being tested, only the first one to appear in the text was considered.
We excluded meeting abstracts and papers that either did not test a hypothesis or for which we lacked sufficient information to determine the outcome. (p.~8)
\end{quote}

Like Fanelli (2010), we coded hypotheses as having received \enquote{support}, \enquote{partial support}, or \enquote{no support}, which was recoded into a binary \enquote{support} (full or partial) vs \enquote{no support} variable for the analysis.
Coding disagreements between full and partial support were deemed minor since they would not affect the final results. Thus, only disagreements affecting the binary support/no support classification were treated as major and resolved through discussion.

Before preregistering our study, we conducted a pilot to assess if we could employ Fanelli's method successfully.
Originally we had planned to first reproduce his results on the same sample of Psychiatry/Psychology articles used in Fanelli (2010).
Unfortunately the author refused to share the original data (or even a list of the coded articles) with us.
Instead, we received an excerpt which contained data for 11 records from the original sample, but no reference information of the coded articles (personal communication, 5th October 2018).
We were able to find these 11 articles based on the hypothesis quotes that had been coded, and used them as a pilot sample along with 10 randomly selected Registered Reports.
MS and AS independently coded all 21 pilot articles with only one major disagreement in each group.
In the standard reports group, this disagreement was also the only case of major disagreement with Fanelli's original coding, which we deemed satisfying to proceed.

Based on our experiences during the pilot, we added one coding criterion:
If the first hypothesis mentioned in a paper was not explicitly tested but subsequently divided into sub-hypotheses that were tested, we would code the first \emph{tested} hypothesis rather than the first hypothesis mentioned in the text.
In Registered Reports we coded the first preregistered hypothesis, thus excluding unregistered pilot studies.
MS coded all papers in the sample, AS double-coded all papers MS had found difficult to code or could not code (\(24\) RRs and \(47\) SRs).
Only 3 disagreements were major (Cohen's kappa = .808) and subsequently resolved by discussion; 15 were minor (disagreement between \enquote{support} and \enquote{partial support}).
We had preregistered that AS would additionally code a random subset of both groups, but decided against it because the number of double-coded papers seemed sufficient after double-coding only the difficult cases.

@@

We also wanted to code if a study was a replication of a previously published one:
We expected a much larger proportion of Registered Reports to be direct replications, many of which may have been motivated by scepticism of the original study.
A lower positive result rate in Registered Reports could then be an effect of failed replications rather than an effect of safeguards against QRPs and publication bias.
After an initial coding attempt with ill-defined coding criteria had led to too many disagreements (described further in the Appendix), we developed the following strategy (not pre-registered):
We searched the full texts of all papers for the string \enquote{replic\(^\ast\)} (cf. Makel, Plucker, \& Hegarty, 2012; Köhler \& Cortina, 2019; Mueller-Langer, Fecher, Harhoff, \& Wagner, 2019; Pridemore, Makel, \& Plucker, 2018) and, for papers that did contain it, determined whether the coded hypothesis was a close replication with the goal to verify a previously published result.
Conceptual replications and internal replications (replication of a study in the same paper) were not counted as replications in this narrow sense, since both are more likely to be motivated by the goal to build on previous work than by scepticism.
AS coded all papers, DL double-coded 32 Registered Reports (\(45.07 \%\)) and 99 standard reports (\(65.13 \%\)).
There were 5 disagreements (Cohen's kappa = .878), all were resolved by discussion.

\hypertarget{additional-measures}{%
\subsubsection{Additional measures}\label{additional-measures}}

All additional measures we collected but have not described thus far were either auxiliary variables to facilitate the coding process or earlier versions of the variables discussed above.
All of these are documented in the Appendix and in our shared dataset and codebook.

>>>>

\usepackage{float}
\usepackage{framed}
\usepackage{caption}
\usepackage{setspace}
\captionsetup[figure]{font={stretch=1, small}, skip=10pt}
\captionsetup[textbox]{name=Box,labelsep=period,labelfont=it}
\newfloat{textbox}{thp}{lop}
\floatname{textbox}{Box}
\usepackage[most]{tcolorbox}
\definecolor{electricviolet}{rgb}{0.56, 0.0, 1.0}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[shorthands=off,main=british]{babel}
\else
  % load polyglossia as late as possible as it *could* call bidi if RTL lang (e.g. Hebrew or Arabic)
  \usepackage{polyglossia}
  \setmainlanguage[variant=british]{english}
\fi

@@

\abstract{
\vspace{0.4cm} \begin{tcolorbox}[colback=white,colframe=electricviolet,coltext=electricviolet,
   fontupper=\normalsize,borderline={0.3mm}{0.3mm}{white}]
 The present version of this manuscript has been accepted for publication at \textsl{Advances in Methods and Practices in Psychological Science}. Please cite as:
  \vspace{0.2cm}
 \begin{center}
 Scheel, A. M., Schijen, M., \& Lakens, D. (in press). An excess of positive results: Comparing the standard Psychology literature with Registered Reports. \textsl{Advances in Methods and Practices in Psychological Science}.
 \end{center}
\end{tcolorbox} \vspace{0.5cm}

Selectively publishing results that support the tested hypotheses (`positive' results) distorts the available evidence for scientific claims. For the past decade, psychological scientists have been increasingly concerned about the degree of such distortion in their literature. A new publication format has been developed to prevent selective reporting: In Registered Reports, peer review and the decision to publish take place before results are known. We compared the results in published Registered Reports (N = 71 as of November 2018) with a random sample of hypothesis-testing studies from the standard literature (N = 152) in Psychology. Analysing the first hypothesis of each paper, we found \(96\%\) positive results in standard reports, but only \(44\%\) positive results in Registered Reports. We discuss possible explanations for this large difference and suggest that a plausible factor is the reduction of publication bias and/or Type-1 error inflation in the Registered-Reports literature.
}

@@

If the scientific literature were a faithful representation of the research scientists conduct, a cumulative science would be a powerful tool to infer what is true about the world.
When random error is the only threat to the accuracy of individual findings, aggregating across many findings allows inferences about the presence and size of effects with a certain reliability.
But when published findings are systematically biased, cumulative science breaks down:
Unlike random error, bias does not cancel out when aggregating across studies\(\,\)---\(\,\)in the worst case it accumulates, leading us away from the truth rather than towards it.
Unfortunately, there is reason to believe that the Psychology literature is not a faithful representation of all research psychologists conduct.

Since the 1950s, scientists have repeatedly noted a suspiciously high \enquote{success} rate in Psychology:
Studying 362 empirical articles published in four Psychology journals in 1955/56, Sterling (1959) found that \(97.28\%\) of studies using significance tests rejected the null hypothesis.
A later replication of this study reported \(95.56\%\) statistically significant results in articles from 1986/87 (Sterling, Rosenbaum, \& Weinkam, 1995).
Similarly, a seminal study by Fanelli (2010) analysed authors' verbal conclusions in hypothesis-testing papers sampled from the literatures of 20 disciplines and found that \(91.5\%\) of papers published in Psychology claimed support for their first hypothesis\(\,\)---\(\,\)the highest estimate of all disciplines in the study.
For these percentages to be a realistic representation of the research psychologists conduct, both statistical power and the proportion of true hypotheses (i.e., the prior probability that the null hypothesis is false) that are tested must exceed \(90\%\).
Put differently, nearly all predictions researchers make must be correct, and either the studied effects or the used samples (given the same design) must consistently be very large.
These two assumptions appear highly implausible a priori, and available evidence on average statistical power in the literature shows that at least one does not hold (e.g., Szucs \& Ioannidis, 2017).

@@

A more plausible explanation for these numbers may be a selection bias towards statistically significant results in the published literature.
We can distinguish two broad categories of bias: \enquote{publication bias} and \enquote{questionable research practices}.
Publication bias describes publishing behaviours that give manuscripts which find support for their tested hypotheses a higher chance of being published than manuscripts with \enquote{negative} results.
These include editors and reviewers selectively rejecting manuscripts with negative results (``reviewer bias'', Greenwald, 1975; Mahoney, 1977) and researchers deciding not to submit studies with negative results for publication (``file-drawering''; Rosenthal, 1979).
Questionable research practices (QRPs) describe research behaviours that make evidence in favour of a certain conclusion look stronger than it is (typically, though not always, leading to more false positives; see Lakens, 2019).
These include presenting unexpected results as having been predicted \emph{a priori} (HARKing, short for ``hypothesising after results are known''; Kerr, 1998) and exploiting flexibility in data analysis to obtain statistically significant results (``\emph{p}-hacking''; Simmons, Nelson, \& Simonsohn, 2011).
Evidence for both categories of bias exist:
Publication bias has been observed in peer review (Atkinson, Furlong, \& Wampold, 1982; Mahoney, 1977) and in longitudinal data from an NSF grant programme that found a file-drawering effect for studies with negative results (Franco, Malhotra, \& Simonovits, 2014, 2016); and QRPs have been admitted by scientists in several survey studies (Agnoli, Wicherts, Veldkamp, Albiero, \& Cubelli, 2017; Fiedler \& Schwarz, 2016; Fraser, Parker, Nakagawa, Barnett, \& Fidler, 2018; John, Loewenstein, \& Prelec, 2012; Makel, Hodges, Cook, \& Plucker, 2019).

Some have argued that negative results are often uninformative or the result of low-quality research and should not be published at the same rate as positive results to avoid cluttering the literature (e.g., Cleophas \& Cleophas, 1999; Baumeister, 2016; Mitchell, 2014).
If most negative results that are currently missing from the literature are indeed due to immature ideas or poor methods, a literature that selects studies based on \emph{quality} instead of results should contain a similar proportion of positive results as the current one.
How many positive and negative results would such an unbiased literature contain in reality?
We investigated this question by comparing the rate of positive results in the Psychology literature to studies published in a new format designed to minimise publication bias and QRPs: Registered Reports.

@@

An increasingly popular proposal to reduce bias is preregistration, where authors register a time-stamped protocol of their hypotheses, methods, and analysis plan before data collection (for a historical overview, see Wiseman, Watt, \& Kornbrot, 2019).
Preregistration is thought to mitigate QRPs by preventing HARKing (hypotheses must be stated before results are known) and by reducing the risk of \emph{p}-hacking via restricted flexibility in data analysis.
However, preregistration does not prevent file-drawering or reviewer bias and may thus be insufficient to fight publication bias (Goldacre et al., 2016; Rasmussen, Lee, \& Bero, 2009; but see Kaplan \& Irvin, 2015).
A more effective safeguard against both publication bias and QRPs is promised by Registered Reports (Chambers \& Tzavella, 2020).

Registered Reports (RRs) are a publication format with a restructured submission timeline:
Before collecting data, authors submit a study protocol containing their hypotheses, planned methods, and analysis pipeline, which undergoes peer review.
If successful, the journal commits to publishing the final article following data collection, regardless of whether the hypotheses are supported (\enquote{in-principle acceptance}).
The authors then collect and analyse the data and complete the final report.
The final report is peer-reviewed again, but this time only to ensure that the the registered plan was adhered to and stated conclusions are justified (and, if applicable, that the data pass pre-specified quality checks).
Registered Reports thus combine an antidote to QRPs (preregistration) with an antidote to publication bias, because studies are selected for publication before their results are known.
Since its introduction in 2013, the format has rapidly gained popularity and is offered by 256 journals at the time of writing (\url{http://cos.io/rr}).

In addition to reducing bias, Registered Reports are designed to ensure high standards for research quality.
First, pre-data peer review increases the chance that methodological flaws and immature ideas will be identified and addressed before a study is conducted.
Second, authors typically have to include outcome-neutral control conditions that allow verifying data quality once results are in (studies failing these quality checks may be rejected).
And third, many journals offering Registered Reports require that hypothesis tests are planned with high statistical power, reducing the risk of false negatives (e.g., \(90\%\) power for a given effect size of interest\footnote{An overview of the requirements specified by each participating journal is available at \url{https://docs.google.com/spreadsheets/d/1D4_k-8C_UENTRtbPzXfhjEyu3BfLxdOsn9j-otrO870}}).

@@

The goal of our study was to test if Registered Reports in Psychology have a lower positive result rate than articles published in the traditional way (henceforth \enquote{standard reports}, SRs), and to estimate the size of this potential difference.
Because the standards for research quality in Registered Reports are at least equal to ordinary peer review, and the statistical power requirements may exceed those in the standard literature (Maxwell, 2004; Szucs \& Ioannidis, 2017), such a difference would be unlikely to be due to \enquote{failed} studies or false negatives.
Barring large confounfds, such as substantial differences in the prior probability of hypotheses tested in Registered Reports versus the standard literature, a much lower positive result rate in Registered Reports might then indicate that publication bias is not a desirable filter for poorly conducted studies, and that we ought to worry about high-quality negative results we are missing because of it.

We set out to compare all published Registered Reports in Psychology with a new sample of standard reports obtained by replicating Fanelli (2010).
Fanelli searched for articles containing the phrase \enquote{test\(^\ast\) the hypothes\(^\ast\)}, drew a random sample of 150 articles per discipline, and coded if the first hypothesis in each article had been supported or not.
For standard reports we used the same sampling method (restricted to the Psychology discipline), for Registered Reports we relied on a database curated by the Center for Open Science (COS).
We chose this method because Fanelli's 2010 and 2012 studies (both use the same coding method) have been highly influential, and because it can easily be applied to a large set of studies.
Because we expected many more Registered Reports than standard reports to be close replications of earlier studies\(\,\)---\(\,\)and perhaps motivated by scepticism of the original results\(\,\)---\(\,\)we additionally examined the role of replications in our analysis.

In a recent commentary, Allen and Mehler (2019) reported a similar investigation:
With a self-developed coding method, they surveyed the 127 biomedical and Psychology Registered Reports listed in the COS database as of September 2018 and found \(60.5\%\) unsupported hypotheses across all included Registered Reports (counting all hypotheses in each paper).
A major advantage of our study, which was planned around the same time (we were unaware of Allen and Mehler's parallel efforts), is the ability to directly compare Registered Reports with the standard literature.
In addition, we replicate Fanelli (2010) and provide data to evaluate his method: The search term \enquote{test\(^\ast\) the hypothes\(^\ast\)} might introduce selection effects, meaning that results obtained this way may not generalise to hypothesis-testing studies that do not use this phrase.
To this end, we coded the phrases used to introduce hypotheses in Registered Reports, analysed how many of them would have been detected with Fanelli's search term, and compiled a list of alternative search terms to test the generalisability of Fanelli's results in the future.
Finally, we share a rich dataset containing the exact quotes of hypotheses and conclusions on which we based our judgements, as well as detailed descriptions of our sampling and coding procedure (see Appendix).
This allows others to verify (or contest) our results and can hopefully provide an interesting resource for future meta-scientific research.

@@

After conducting a pilot to test the planned procedure, we preregistered our study (\url{https://osf.io/sy927/}).
Methods and analyses described here were preregistered unless otherwise noted.
Our online materials include an Appendix with fine-grained methodological details and an annotated preregistration document with detailed comparisons to the eventual procedure (\url{https://osf.io/dbhgr}).
Appendix and open dataset also list all measures we collected but do not describe here (all of which were either auxiliary variables to facilitate the coding process or earlier versions of the variables discussed here).

@@

We used the same method as Fanelli (2010) to obtain a new sample of standard reports in Psychology, but restricted year of publication to 2013-2018 to match the sample to the Registered Reports population.
We excluded papers in both groups if they were incomplete, unpublished, or retracted (e.g., meeting abstracts, study protocols without results), if they did not test a hypothesis, or if they contained insufficient information to reach a coding decision.
An overview of the sampling process and all exclusions is shown in Figure~\ref{fig:sampling}.

The sample size of standard reports was pre-specified to replicate the one used by Fanelli (2010), \(n = 150\), since it matched the maximum number of Registered Reports available at the time (\(n = 151\), see below) and piloting indicated that the required coding time would just fit our resource constraints.
Standard reports were selected by searching the 633 journals listed under \enquote{Psychiatry/Psychology} in the Essential Science Indicators database for papers published between 2013 and 2018 that contained the phrase \enquote{test\(^\ast\) the hypothes\(^\ast\)} in title, abstract, or keywords.
We then randomly selected 150 papers from the 1919 papers that resulted from this search. Excluded papers were replaced by resampling twice (this decision was not preregistered), which led to accidental oversampling and a final sample size of 152 (see Fig.~\ref{fig:sampling}).

@@

The sample size of Registered Report was determined by our goal to include all published Registered Reports in the field of Psychology that tested at least one hypothesis, regardless of whether they used the phrase \enquote{test\(^\ast\) the hypothes\(^\ast\)}.
Registered Reports were selected through a Registered-Reports database curated by the Center for Open Science\footnote{\url{https://www.zotero.org/groups/479248/osf/items/collectionKey/KEJP68G9}} (retrieved 19th November 2018).
After excluding non-Psychology papers, we verified that all remaining papers were indeed Registered Reports by consulting the journal submission guidelines, relevant editorials, or contacting the editors directly.
Papers were counted as Registered Reports if we could establish that these submissions had been reviewed and received in-principle acceptance before the data collection (or analyses) of all studies in the paper had been conducted (in accordance with \url{https://cos.io/rr}).
We excluded 80 of the 151 entries in the COS Registered Reports database, leaving 71 Registered Reports for the final analysis (see Fig.~\ref{fig:sampling}).
Note that we excluded all eight \enquote{Registered Replication Reports} (RRRs; Simons, Holcombe, \& Spellman, 2014; Simons, 2018) in our sample because this format explicitly focuses on effect size estimation and not hypothesis testing (``Registered Replication Reports,'' n.d., decision was not preregistered).

@@

The main dependent variable was whether the first hypothesis was supported or not, as reported by the authors.
We tried to follow Fanelli's coding procedure as closely as possible:

\begin{quote}
By examining the abstract and/or full- text, it was determined whether the authors of each paper had concluded to have found a positive (full or partial) or negative (null or negative) support.
If more than one hypothesis was being tested, only the first one to appear in the text was considered.
We excluded meeting abstracts and papers that either did not test a hypothesis or for which we lacked sufficient information to determine the outcome. (Fanelli, 2010, p. 8)
\end{quote}

In Registered Reports, we coded the first \emph{preregistered} hypothesis, thus excluding unregistered pilot studies.
The coding procedure was identical for both article formats in all other respects.
Coding disagreements between \enquote{full} and \enquote{partial} support were deemed minor since they would not affect the final results.
Thus, only disagreements affecting the binary support (full or partial) vs no support classification were treated as major and resolved through discussion.
MS coded all papers in the sample, AS double-coded all papers MS had found difficult to code or could not code (\(24\) RRs and \(47\) SRs).
Only 3 disagreements were major (Cohen's kappa = .808) and subsequently resolved by discussion; 15 were minor (disagreement between \enquote{support} and \enquote{partial support}).
We overturned the preregistered plan that AS would additionally code a random subset of both groups, because the number of double-coded papers seemed sufficient after double-coding only the difficult cases.
Because removing all indicators that could have identified Registered Reports as such from their full texts would have been practically impossible, coding was not blind to publication format (Registered Report vs standard report).

@@

We expected a large proportion of Registered Reports to be replications, many of which may have been motivated by scepticism of the original study.
Because this circumstance alone could potentially lead to a lower positive result rate in Registered Reports, we additionally coded if hypotheses were close replications of previously published work.
Due to ill-specified coding criteria in our preregistration (see Appendix), we used an unregistered coding strategy:
We determined whether the coded hypothesis of papers whose full text contained the string \enquote{replic\(^\ast\)} (cf. Makel, Plucker, \& Hegarty, 2012; Mueller-Langer, Fecher, Harhoff, \& Wagner, 2019) was a close replication with the goal to verify a previously published result.
Conceptual replications and internal replications (replication of a study in the same paper) were not counted as replications in this narrow sense, since both are more likely to be motivated by the goal to build on previous work than by scepticism.
AS coded all papers, DL double-coded 32 Registered Reports (\(45.07 \%\)) and 99 standard reports (\(65.13 \%\)).
There were 5 disagreements (Cohen's kappa = .878), all were resolved by discussion.
